Commutative Character Sheaves

### 2015-11-13 followup.tex
align* for b functions
In the sense of ECS1...

Let $G$ be a smooth group scheme over $k$, as above.
Let $H$ be a group scheme and write $n : H \times H \to H$ for the multiplication morphism.
Let $a : H \times G\to G$ be a group action compatible with the group structure on $G$ and write $p : H\times G \to G$ for projection. 
Consider the morphisms
\[
\begin{tikzcd}
H \times H \times G 
\arrow[shift left=4]{r}{b_1, b_2, b_3} 
\arrow{r}{}
\arrow[shift right=4]{r}{} 
& H \times G 
\arrow[shift left=2]{r}{a}
\arrow[shift right=2]{r}[swap]{p}
 & G 
\end{tikzcd}
\]
defined by $b_1(h_1,h_2,g) = (n(h_1,h_2),g)$,  $b_2(h_1,h_2,g) = (h_1,a(h_2,g))$ and $b_3(h_1,h_2,g) = (h_2,g)$.
Then, $a\circ b_1 = a\circ b_2$ and $a\circ b_3 = p\circ b_2$ and $p\circ b_1 = p\circ b_3$.
Define $s : G\to H\times G$ by $s(g) = (1,g)$.
An $H$-equivariant Weil local sytem on $G$ is a Weil local system $\cs{L}$ on $G$ together with an isomorphism  
\[
\nu : a^*\cs{L} \to p^*\cs{L}
\] 
of Weil local systems on $H\times G$ such that 
\begin{equation}\label{E1}
s^*(\nu) = \id_{\cs{L}}
\end{equation}
and the following diagram of isomorphisms of local systems on $H\times H\times G$ commutes,
\begin{equation}\label{E2}
\begin{tikzcd}
\ &  \arrow{dl}{a\circ b_1 = a\circ b_2}  b_2^*  a^*\, \mathcal{L} \arrow{rr}{b_2^*(\nu)} && b_2^* p^*\, \mathcal{L} \arrow{dr}[swap]{p\circ b_2 = a\circ b_3} & \\
b_1^* a^*\, \mathcal{L} \arrow{dr}{b_1^*(\nu)} &&&&   \arrow{dl}[swap]{b_3^*(\nu)} b_3^* a^*\, \mathcal{L} \\
& b_1^* p^*\, \mathcal{L}  && \arrow{ll}[swap]{p\circ b_3 = p\circ b_1} b_3^* p^*\, \mathcal{L}, & 
\end{tikzcd}
\end{equation}
In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from the equations above; so, for example, the top left isomorphism comes from $b_1^* a^* \iso b_2^* a^*$ since $a\circ b_1 = a\circ b_2$.
\iffalse
On stalks, this condition is ...
\[
\begin{tikzcd}
\ &  \cs{L}_{h_1\cdot(h_2\cdot g)} \arrow{r}{\nu_{h_1,h_2\cdot g}} & \cs{L}_{h_2\cdot g} & \\
\cs{L}_{(h_1 h_2) \cdot g} \arrow{dr}[swap]{\nu_{(h_1h_2),g}} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{\nu_{h_2,g}} \cs{L}_{h_2\cdot g} \\
& \cs{L}_g \arrow[equal]{r} & \cs{L}_g & 
\end{tikzcd}
\]
\fi
Morphisms of $H$-equivariant Weil local systems $(\cs{L},\nu)\to (\cs{L}',\nu')$ are morphisms of Weil local systems $\alpha: \cs{L}\to \cs{L}'$ for which the diagram
\begin{equation}\label{E3}
\begin{tikzcd}
\arrow{d}[swap]{\nu} a^*\cs{L} \arrow{r}{a^*(\alpha)} & a^*\cs{L}' \arrow{d}{\nu'} \\
p^*\cs{L} \arrow{r}{p^*(\alpha)} & p^*\cs{L}'
\end{tikzcd}
\end{equation}
commutes.
This defines $\Loc_H(G)$, the category of $H$-equivariant Weil local systems on $G$.

@@

An $H$-equivariant linear character sheaf on $G$ is a triple $(\cs{L},\mu, \nu)$ where $(\cs{L},\mu)$ is a linear character sheaf and $\nu$ is compatible with $\mu$ in the sense \todo{of...}. 
Consider the following morphisms: $c_0 : H\times G \times G\to H\times G \times H \times G$ defined by $c_0(h,g_1,g_2)\ceq(h,g_1,h,g_2)$;
$c_1 : H \times G\times G \to G\times G$ defined by $c_1(h, g_1, g_2) \ceq (a(h,g_1),a(h,g_2))$;  $c_2 : H \times G\times G \to H\times G$ defined by $c_2(h,g_1,g_2) \ceq (h, m(g_1,g_2))$; and $c_3 : H \times G\times G \to G\times G$ defined by $c_3(h, g_1, g_2) = (g_1, g_2)$. 
Then $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ if $(\cs{L},\mu)$ is a linear character sheaf on $G$ and the following diagram of Weil local systems on $H \times G\times G$ commutes.
\begin{equation}\label{ECS1}
\begin{tikzcd}
\ & \arrow{dl}{c_2\circ a = m\circ c_1}  c_2^* a^* \cs{L} \arrow{r}{c_2^*(\nu)} & c_2^* p^* \cs{L} \arrow{dr}[swap]{p\circ c_2 = m\circ c_3}  &  \\
\arrow{d}[swap]{c_1^*(\mu)} c_1^* m^* \cs{L} &&& c_3^* m^*\cs{L} \arrow{d}{c_3^*(\mu)} \\
c_1^*(\cs{L}\boxtimes \cs{L}) \arrow{dr}{p_i\circ c_1 = a\circ p_i\circ c_0} &&& \arrow{dl}[swap]{p\circ p_i\circ c_0 = p_i \circ c_3} c_3^*(\cs{L}\boxtimes \cs{L}) \\
 & c_0^*(a^*\cs{L}\boxtimes a^*\cs{L}) \arrow{r}{c_0^*(\nu\boxtimes \nu)} & c_0^*(p^*\cs{L} \boxtimes p^*\cs{L}) & 
\end{tikzcd}
\end{equation}
\iffalse
On stalks, this condition is
\[
\begin{tikzcd}
\arrow{d}[swap]{\mu_{(h\cdot g_1, h\cdot g_2)}} \cs{L}_{(h\cdot g_1)(h\cdot g_2)} & \arrow[equal]{l}  \cs{L}_{h\cdot(g_1 g_2)} \arrow{r}{\nu_{(h, g_2 g_2)}} & \cs{L}_{g_1 g_2} \arrow[equal]{r} & \cs{L}_{g_1 g_2} \arrow{d}{\mu_{(g_1,g_2)}} \\
\cs{L}_{h\cdot g_1}\otimes \cs{L}_{h\cdot g_2} \arrow[equal]{r} & \cs{L}_{h\cdot g_1}\otimes \cs{L}_{h\cdot g_2} \arrow{r}{\nu_{(h,g_1)}\otimes \nu_{(h,g_2)}} & \cs{L}_{g_1}\otimes \cs{L}_{g_2} & \arrow[equal]{l} \cs{L}_{g_1} \otimes \cs{L}_{g_2},
\end{tikzcd}
\]
for all $(h,g_1,g_2)\in H\times G\times G$.
\fi

>>>>

Let $G$ be a smooth group scheme over $k$, as above.
Let $H$ be a group scheme and write $n : H \times H \to H$ for the multiplication morphism.
Let $a : H \times G\to G$ be a group action compatible with the group structure on $G$ and write $p : H\times G \to G$ for projection. 
Consider the morphisms
\[
\begin{tikzcd}
H \times H \times G 
\arrow[shift left=4]{r}{b_1, b_2, b_3} 
\arrow{r}{}
\arrow[shift right=4]{r}{} 
& H \times G 
\arrow[shift left=2]{r}{a}
\arrow[shift right=2]{r}[swap]{p}
 & G 
\end{tikzcd}
\]
defined by 
\begin{align*}
b_1(h_1,h_2,g) &= (h_1h_2,g) \\
b_2(h_1,h_2,g) &= (h_1,h_2g) \\
b_3(h_1,h_2,g) &= (h_2,g).
\end{align*}
Then, $a\circ b_1 = a\circ b_2$ and $a\circ b_3 = p\circ b_2$ and $p\circ b_1 = p\circ b_3$.
Define $s : G\to H\times G$ by $s(g) = (1,g)$.
An $H$-equivariant Weil local sytem on $G$ is a Weil local system $\cs{L}$ on $G$ together with an isomorphism  
\[
\nu : a^*\cs{L} \to p^*\cs{L}
\] 
of Weil local systems on $H\times G$ such that 
\begin{equation}\label{E1}
s^*(\nu) = \id_{\cs{L}}
\end{equation}
and the following diagram of isomorphisms of local systems on $H\times H\times G$ commutes,
\begin{equation}\label{E2}
\begin{tikzcd}
\ &  \arrow{dl}{a\circ b_1 = a\circ b_2}  b_2^*  a^*\, \mathcal{L} \arrow{rr}{b_2^*(\nu)} && b_2^* p^*\, \mathcal{L} \arrow{dr}[swap]{p\circ b_2 = a\circ b_3} & \\
b_1^* a^*\, \mathcal{L} \arrow{dr}{b_1^*(\nu)} &&&&   \arrow{dl}[swap]{b_3^*(\nu)} b_3^* a^*\, \mathcal{L} \\
& b_1^* p^*\, \mathcal{L}  && \arrow{ll}[swap]{p\circ b_3 = p\circ b_1} b_3^* p^*\, \mathcal{L}, & 
\end{tikzcd}
\end{equation}
In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from the equations above; so, for example, the top left isomorphism comes from $b_1^* a^* \iso b_2^* a^*$ since $a\circ b_1 = a\circ b_2$.
\iffalse
On stalks, this condition is ...
\[
\begin{tikzcd}
\ &  \cs{L}_{h_1\cdot(h_2\cdot g)} \arrow{r}{\nu_{h_1,h_2\cdot g}} & \cs{L}_{h_2\cdot g} & \\
\cs{L}_{(h_1 h_2) \cdot g} \arrow{dr}[swap]{\nu_{(h_1h_2),g}} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{\nu_{h_2,g}} \cs{L}_{h_2\cdot g} \\
& \cs{L}_g \arrow[equal]{r} & \cs{L}_g & 
\end{tikzcd}
\]
\fi
Morphisms of $H$-equivariant Weil local systems $(\cs{L},\nu)\to (\cs{L}',\nu')$ are morphisms of Weil local systems $\alpha: \cs{L}\to \cs{L}'$ for which the diagram
\begin{equation}\label{E3}
\begin{tikzcd}
\arrow{d}[swap]{\nu} a^*\cs{L} \arrow{r}{a^*(\alpha)} & a^*\cs{L}' \arrow{d}{\nu'} \\
p^*\cs{L} \arrow{r}{p^*(\alpha)} & p^*\cs{L}'
\end{tikzcd}
\end{equation}
commutes.
This defines $\Loc_H(G)$, the category of $H$-equivariant Weil local systems on $G$.

@@

An $H$-equivariant linear character sheaf on $G$ is a triple $(\cs{L},\mu, \nu)$ where $(\cs{L},\mu)$ is a linear character sheaf and $\nu$ is compatible with $\mu$ in the sense of \eqref{ECS1}.
Consider the following morphisms: $c_0 : H\times G \times G\to H\times G \times H \times G$ defined by $c_0(h,g_1,g_2)\ceq(h,g_1,h,g_2)$;
$c_1 : H \times G\times G \to G\times G$ defined by $c_1(h, g_1, g_2) \ceq (a(h,g_1),a(h,g_2))$;  $c_2 : H \times G\times G \to H\times G$ defined by $c_2(h,g_1,g_2) \ceq (h, m(g_1,g_2))$; and $c_3 : H \times G\times G \to G\times G$ defined by $c_3(h, g_1, g_2) = (g_1, g_2)$. 
Then $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ if $(\cs{L},\mu)$ is a linear character sheaf on $G$ and the following diagram of Weil local systems on $H \times G\times G$ commutes.
\begin{equation}\label{ECS1}
\begin{tikzcd}
\ & \arrow{dl}{c_2\circ a = m\circ c_1}  c_2^* a^* \cs{L} \arrow{r}{c_2^*(\nu)} & c_2^* p^* \cs{L} \arrow{dr}[swap]{p\circ c_2 = m\circ c_3}  &  \\
\arrow{d}[swap]{c_1^*(\mu)} c_1^* m^* \cs{L} &&& c_3^* m^*\cs{L} \arrow{d}{c_3^*(\mu)} \\
c_1^*(\cs{L}\boxtimes \cs{L}) \arrow{dr}{p_i\circ c_1 = a\circ p_i\circ c_0} &&& \arrow{dl}[swap]{p\circ p_i\circ c_0 = p_i \circ c_3} c_3^*(\cs{L}\boxtimes \cs{L}) \\
 & c_0^*(a^*\cs{L}\boxtimes a^*\cs{L}) \arrow{r}{c_0^*(\nu\boxtimes \nu)} & c_0^*(p^*\cs{L} \boxtimes p^*\cs{L}) & 
\end{tikzcd}
\end{equation}
\iffalse
On stalks, this condition is
\[
\begin{tikzcd}
\arrow{d}[swap]{\mu_{(h\cdot g_1, h\cdot g_2)}} \cs{L}_{(h\cdot g_1)(h\cdot g_2)} & \arrow[equal]{l}  \cs{L}_{h\cdot(g_1 g_2)} \arrow{r}{\nu_{(h, g_2 g_2)}} & \cs{L}_{g_1 g_2} \arrow[equal]{r} & \cs{L}_{g_1 g_2} \arrow{d}{\mu_{(g_1,g_2)}} \\
\cs{L}_{h\cdot g_1}\otimes \cs{L}_{h\cdot g_2} \arrow[equal]{r} & \cs{L}_{h\cdot g_1}\otimes \cs{L}_{h\cdot g_2} \arrow{r}{\nu_{(h,g_1)}\otimes \nu_{(h,g_2)}} & \cs{L}_{g_1}\otimes \cs{L}_{g_2} & \arrow[equal]{l} \cs{L}_{g_1} \otimes \cs{L}_{g_2},
\end{tikzcd}
\]
for all $(h,g_1,g_2)\in H\times G\times G$.
\fi
